Quantitative Models for Retirement Risk in Professional Tennis

### 2012-12-19 retrisk.tex
added camwa formatting

%% This file is to be used as a template for your submission. 
%% Rename this file and replace the text with the text of 
%% your manuscript.
%%
%% The standard LaTeX document class "article" is recommended. 
%% Use options letterpaper and 12pt.
\documentclass[letterpaper,12pt]{article}

%% This is the recommended preamble for your document.

%% Load De Gruyter specific settings 
\usepackage{dgjournal}

@@

%% Use natbib with these recommended options
\usepackage[authoryear,comma,longnamesfirst,sectionbib]{natbib} 
\usepackage{url}

@@

%% Start your document body here
\begin{document}

%% Do NOT include any fronmatter information; including the title, author names,
%% institutes, acknowledgments and title footnotes (author information, funding
%% sources, etc.). Start the document with the first section or paragraph of
%% the article.

@@

We executed the Nelder-Mead method a number of times under the same conditions and took the means of the approximations found for our three parameters each time as our chosen values.  Remember, $c$ is the per point injury probability, $\lambda$ is the point-level retirement risk magnitude exponential distribution rate parameter, and $\rho$ is the injury recovery factor.  We find:

@@

% BibTeX support
\bibliographystyle{DeGruyter}
\bibliography{paper}

>>>>

\documentclass[letterpaper,12pt]{elsarticle}

@@

\usepackage{url}

@@

% Horizontal line for title page
\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}

\begin{document}

\title{Quantitative Models for Retirement Risk in Professional Tennis}

\author[icl]{A.C.J.˜Cutmore\corref{cor1}}
\ead{adam.cutmore08@imperial.ac.uk}

\author[icl]{W.J.˜Knottenbelt}
\ead{w.knottenbelt@imperial.ac.uk}

\cortext[cor1]{Corresponding author}

\address[icl]{Imperial College London, South Kensington Campus, Exhibition Road,
London, SW7 2AZ, UK}

\date{\today}

\begin{abstract}

Tennis attracts both spectators and speculators.  Indeed, every
on-court development impacts on in-play financial markets.  For
singles matches, sophisticated traders make use of quantitative
models.  These yield the probability of each player winning the match
given the current score and the probability of each player winning a
point on serve.  Significantly, these models ignore retirement risk,
which can drastically and rapidly alter in-play odds. The precise
impact on a market depends on that market.s payout policy in the case
of player retirement.

This paper proposes novel quantitative models for the in-play
evolution of retirement risk due to injury and the corresponding
impacts on in-play match outcome markets under different retirement
payout policies. Injury occurrence is assumed to be a Bernoulli
process, with a magnitude sampled from a truncated exponential
distribution. Retirement risk is propagated from one point to another
subject to a damping parameter that reflects a player's ability to
``run off'' an injury.

An important practical challenge is to parameterise our models given a
score feed and odds data for two match outcome markets with different
retirement policies. We demonstrate the feasibility of not only
inferring model parameters from synthetic data effectively but also of
mimicking real in-play markets.

\end{abstract}

\begin{keyword}
tennis modelling \sep in-play betting markets \sep retirement risk \sep injuries
\end{keyword}

\maketitle

@@

We executed the Nelder-Mead method a number of times under the same conditions and took the means of the approximations found for our three input parameters each time as our chosen values.  Remember, $c$ is the per point injury probability, $\lambda$ is the point-level retirement risk magnitude exponential distribution rate parameter, and $\rho$ is the injury recovery factor.  We find:

@@

% BibTeX support
\bibliographystyle{model1a-num-names}
\bibliography{paper}
